Fixing Vulnerabilities Potentially Hinders Maintainability

### 2021-02-08 paper/emse20.tex
final touches to study implications and lessons learned

\textit{\textbf{Prioritize High and Medium Severity:}} Previous research 
exhibits proof that developers prioritize
higher impact vulnerabilities~\cite{10.1145/3133956.3134072}.
Our study shows that vulnerabilities of high and
medium severity should be prioritized in software maintainability tasks
by developers.

\textit{\textbf{Some Types of Vulnerabilities Need More Attention:}} 
Our study attempted at shedding light at the impact 
of different types of vulnerabilities on software maintainability.
Overall, all the CWEs studied in more depth present a negative impact
over $30\%$ on software maintainability. 
\emph{Cross-Site Scripting} (CWE-79) and \emph{Improper 
Restriction of Operations within the Bounds of a Memory Buffer} (CWE-119) 
are less prone to have impact on open-source software maintainability.
Developers should pay special attention to \emph{Improper Input Validation} (CWE-20), 
\emph{Information Exposure} (CWE-200), \emph{Missing Release of Memory after Effective Lifetime} 
(CWE-401) and \emph{Path Traversal} (CWE-22). However, 
more research should be performed to better understand 
the impact of each guideline on each CWE.

>>>>

\textit{\textbf{Prioritize High and Medium Severity:}} Previous research 
exhibits proof that developers prioritize
higher impact vulnerabilities~\cite{10.1145/3133956.3134072}.
Our study shows that vulnerabilities of high and
medium severity should be prioritized in software maintainability tasks.

\textit{\textbf{Some Types of Vulnerabilities Need More Attention:}} 
Our study attempted at shedding light at the impact 
of different types of vulnerabilities on software maintainability.
Overall, all the CWEs under study present a negative impact
over $30\%$ on software maintainability. 
\emph{Cross-Site Scripting} (CWE-79) and \emph{Improper 
Restriction of Operations within the Bounds of a Memory Buffer} (CWE-119) 
are less prone to have impact on open-source software maintainability.
Developers should pay special attention to \emph{Improper Input Validation} (CWE-20), 
\emph{Information Exposure} (CWE-200), \emph{Missing Release of Memory after Effective Lifetime} 
(CWE-401) and \emph{Path Traversal} (CWE-22). However, 
more research should be performed to better understand 
the impact of each guideline on each CWE.
